---
title: "demo post"
categories:
  - R 
  - AdvR answers
description: |
  A new article created using the Distill format.
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
    affiliation: InferenceX
    affiliation_url: https://rgthomaslab.com
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: '`r normalizePath("~/share/library.bib")`'
---

```{r setup, include=FALSE}
options(dplyr.print_max = 1e9)
library(pacman)
p_load(tibble, broom, snakecase, tidyr, data.table,colorout, conflicted,
       purrr,ztable, hrbrthemes,readr, dplyr, magrittr, 
       lubridate, zoo, mi, survival, ggplot2, printr,
       lsmeans, ggthemes,  knitr, xtable, doBy, nlme,
       reshape2,  pander, pwr, tufte)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/work/reports/templates/zz.tools.R')
options(scipen = 1, digits = 2)
knitr::opts_chunk$set(echo = FALSE)
```



# Introduction

My most common usage of the todonotes package, is to insert an uncustomized
todonotes somewhere in a latex document. An example of this usage is the command
Sample reference section reference. [@Pocock2005].

# Methods
A careful reading of the chapter. Reference additional references
including: 

# Results
Notes and offered solutions. 


# References


```{r  include=FALSE}
# clear env: objects and packages
rm(list = ls())
options(knitr.kable.NA = '',dplyr.summarise.inform = FALSE, 
	dplyr.print_max = 1e9,knitr.table.format = "latex")

opts_chunk$set(warning = F, message = F, echo = F, fig.width = 3.2,
       fig.height = 3,  results = "asis", dev = "pdf",
       opts_chunk$set(cache.path = "cache/"))
source("~/work/reports/templates/zz.tools.R")
options(scipen = 1, digits = 2)
```

# Introduction



# Methods

# Results


```{r}
# steps to add a simple table 
# 1) inside R block: create the table in tabyl(), call it tab1
# > dat  %>%  tabyl(var1, var2)
library(kableExtra)
library(janitor)
# 3. kable(tab1, "latex", booktabs = T,escape=FALSE) %>%
# 		kable_styling(latex_options = "striped")   
# 4. zz.figured(tab1)
# 5. outside R block: \newpage \includegraphics[]{./tables/tab1.pdf}
# 6. choose between the two versions. 
# 7. add a caption.  \captionof{figure}{tab1 caption}
tab1 = iris  %>%  
mutate(len = Petal.Length > 1.3)  %>%  
tabyl(len,Species) %>%  
adorn_totals(where = "row") %>%  
adorn_totals(where = "col")   
out = kbl(tab1,format="html",  booktabs = T,escape=FALSE, 
    caption = "tabled visit and week number") %>%
		kable_paper(latex_options = "striped")    
out
# follow with latex outside R chunk
# \includegraphics[]{./tables/tab1.pdf}

```


# Code 
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```

# References
