---
title: "Construct quarto blog"
description: |
  I'm ready to do some blogging. I've worked out the Distill procedure, but it
  seems limiting. I'm going to try to mimic what I have in quarto. 
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
date: 2022-07-22
output:
  distill::distill_article:
    self_contained: false
draft: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Introduction
Start at the quarto ["Get Started"](https://quarto.org/docs/get-started/)
page: Download the latest macos file: ``quarto-1.0.36-macos.pkg``
and install
```sh
open quarto-1.0.36-macos.pkg
```

To initiate the blog navigate to prj directory and run the ``quarto create-project``
command.

```sh
quarto create-project myblog --type website:blog
```
next open Rstudio

create a new project in the ~/prj/qblog directory

in the "build" pane. select "render website"



```{r init, include=FALSE}
# read this snippet in to new blog posts templates written by Distill
# from vim ":r ~/blog/draftpost.Rmd"
# or using sh> cat draftpost.Rmd >> _post/postname/postname.Rmd
# don't forget to add 
# bibliography: /Users/zenn/shr/library.bib
# if including references
# to YAML above  
options(dplyr.print_max = 1e9)
library(pacman)
p_load(rmarkdown, tidyverse,  broom,  lubridate, printr, ggthemes, knitr, pwr)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/shr/zz.tools.R')
options(scipen = 1, digits = 2)

# Introduction


# Methods

# Results

# References





