---
title: "git for the solo data science developer"
description: |
  A short description of the post.
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
date: 2022-07-06
output:
  distill::distill_article:
    self_contained: false
bibliography: /Users/zenn/shr/library.bib
draft: true
---


```{r init, include=FALSE}
# read this snippet in to new blog posts templates written by Distill
# from vim ":r ../../draftpost.Rmd"
# don't forget to add "

# draft: true
# bibliography: /Users/zenn/shr/library.bib
# 
# to YAML above  

options(dplyr.print_max = 1e9)
library(pacman)

p_load(rmarkdown, tidyverse,  broom,  tidyr,  purrr,readr,
       dplyr,  lubridate, zoo,  ggplot2, printr, lsmeans, ggthemes,  knitr,
       nlme, pwr)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/shr/zz.tools.R')
options(scipen = 1, digits = 2)
```

# Introduction

This document chronicles my circuitous journey from old school naming of
sequential drafts with a date stamped name creating a new copy of the program
file each time I started working on it. I wrote a small utility to find the last
Rmd file in a directory, extract the base name and copy to a new file with a
current date stamp. This actually worked reasonably well for being able to "roll
back" an iteration or two if I changed my mind about a feature, or messed up
with the coding and  needed a "fresh" copy. 

However, as I learnt more about git as a version control system the more I
realized I was being naive as to the best approach. Git can be cryptic but its 
able to do everything I needed and much more. The trick was to determine what I
needed as a solo developer in order to be able to try new feature ideas without
corrupting a master version. 

At first the main challenge was to understand the branch and merging process. 

I started with the excellent reference Pro Git by Scott Chacon and Ben Straub https://git-scm.com/book/en/v2.

The first three chapters got me started. 

I simultaneously worked my way through the online tutorial for the vim plugin
Fugitive by Tim Pope. https://dzx.fr/blog/introduction-to-vim-fugitive/

## First question
The first question a solo developer might ask is "Why don't I just use the
master branch to develop in? I can commit when I want to save and roll back if I
need to rework something. 

This is a great question. I'll offer a few pros and cons in the following. 


Sample reference section reference. @Pocock1975a

# Methods

# Results
My most common usage of the todonotes package, is to insert an uncustomized
todonotes somewhere in a latex document. An example of this usage is the command

# References






# Introduction


# Methods

# Results
My most common usage of the todonotes package, is to insert an uncustomized
todonotes somewhere in a latex document. An example of this usage is the command

# References






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.


