---
title: "Configuring neovim as R IDE"
description: |
  A short description of the post.
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
date: 2022-06-13
output:
  distill::distill_article:
    self_contained: false
draft: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.



```{r init, include=FALSE}
# read this snippet in to new blog posts templates written by Distill
# from vim ":r ../../draftpost.Rmd"
# don't forget to add "draft: true" to YAML above
options(dplyr.print_max = 1e9)
library(pacman)

p_load(rmarkdown, tidyverse,  broom,  tidyr,  purrr,readr,
       dplyr,  lubridate, zoo,  ggplot2, printr, lsmeans, ggthemes,  knitr,
       nlme, pwr)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/shr/zz.tools.R')
options(scipen = 1, digits = 2)
```

# Introduction

Sample reference section reference. @Pocock1975a

# Methods

# Results
My most common usage of the todonotes package, is to insert an uncustomized
todonotes somewhere in a latex document. An example of this usage is the command

# References





