---
title: "Project report template (Cxx)"
author: "R.G. Thomas"
date: "`r Sys.Date()`"
fontsize: 11pt
geometry: "left=3cm,right=3in,top=2cm,bottom=2cm"
output:
  pdf_document:
#   toc: true
    number_sections: true
    highlight: tango
    keep_tex: true 
    includes:
      in_header: "/Users/zenn/shr/preamble.tex"
header-includes:
   - \rhead{Cxx project. Trial Design Lab report (draft)}
bibliography: '`r normalizePath("~/share/library.bib")`'
latex_engine: xelatex
---

\hspace{4in}
\fbox{
\parbox{3in}{\Large 
Notes: 
\begin{itemize}
\item mimic grazzi, gill, dimitriadis \\
\item plan: random forest analysis of cognitive data to
find enrichment criteria
\end{itemize}
}
}
\listoftodos


```{r  include=FALSE}
# clear env: objects and packages
rm(list = ls())
wh = which(search()=="package:nvimcom")
if (wh >2) for (x in (wh-1):2) {detach(po = x, force=T)}
rm(x, wh)
options(knitr.kable.NA = '',dplyr.summarise.inform = FALSE, 
	dplyr.print_max = 1e9,knitr.table.format = "latex")
library(pacman)
p_load(janitor, kableExtra,tidyverse, knitr)

opts_chunk$set(warning = F, message = F, echo = F, fig.width = 3.2,
       fig.height = 3,  results = "asis", dev = "pdf",
       opts_chunk$set(cache.path = "cache/"))
source("~/shr/zz.tools.R")
options(scipen = 1, digits = 2)
```

# Introduction
\lipsum[2]
\todo[inline, color=cyan]{The original todo note withouth changed colours.\newline Here's another line.}
\begin{wrapfigure}{r}[.4\textwidth]{.4\textwidth}%
\textit{\sffamily\normalsize\textcolor{gray!50}{
Tornado plot: x-axis participants IDs y-axis study visits plot mean of cumulative
AEs stratified by pre-covid and post-covid study visits (March 12 is
the date we are using as a cut-point: through March 12 is pre-COVID,
after March 12 is post-COVID) }}% 
\end{wrapfigure}
\lipsum[2]

Sample reference section reference. @Pocock1975a

\begin{marginfigure}
\includegraphics[width=3in]{/Users/zenn/prj/images/sudoku-3d-cube.pdf} \caption{test}\label{fig:unnamed-chunk-8}
\end{marginfigure}

# Methods

# Results
My most common usage of the todonotes package, is to insert an uncustomized
todonotes somewhere in a latex document. An example of this usage is the command
\todo{Make a cake \ldots},
\lipsum[1]
\todo[color=green]{Make a pie \ldots},
\lipsum[1] 
\todo{Make a joke \ldots},
\listoftodos


```{r}
# steps to add a simple table 
# 1) inside R block: create the table in tabyl(), call it tab1
# > dat  %>%  tabyl(var1, var2)
# 2. library(kableExtra)
# 3. kable(tab1, "latex", booktabs = T,escape=FALSE) %>%
# 		kable_styling(latex_options = "striped")   
# 4. zz.figured(tab1)
# 5. outside R block: \newpage \includegraphics[]{./tables/tab1.pdf}
# 6. choose between the two versions. 
# 7. add a caption.  \captionof{figure}{tab1 caption}
tab1 = iris  %>%  
mutate(len = Petal.Length > 1.3)  %>%  
tabyl(len,Species) %>%  
adorn_totals(where = "row") %>%  
adorn_totals(where = "col")   
out = kbl(tab1,  booktabs = T,escape=FALSE, 
    caption = "tabled visit and week number") %>%
		kable_paper(latex_options = "striped")    
out
# advanced formatting. if desire to convert table to figure.
zz.figured(tab1)
# follow with latex outside R chunk
# \includegraphics[]{./tables/tab1.pdf}

```

\newpage 
\includegraphics[]{./tables/tab1.pdf}
\captionof{figure}{tabled visit and week number}

# Code 
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```

# References
