---
title: "tools: ranger"
description: |
  A short description of the post.
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
bibliography: /Users/zenn/shr/bibs/ranger_blog_post.bib
date: 2021-12-29
draft: true
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



```{r init, include=FALSE}
options(dplyr.print_max = 1e9)
library(pacman)

p_load(rmarkdown, tidyverse,  broom,  tidyr,  purrr,readr,
       dplyr,  lubridate, zoo,  ggplot2, printr, lsmeans, ggthemes,  knitr,
       nlme, pwr)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/shr/zz.tools.R')
options(scipen = 1, digits = 2)
```



# Introduction

This is another of the continuing articles describing useful tools for the
RGT laboratory. 

Ranger is an alternative to the mac Finder. It runs in the terminal using the
Curses library (expand). I think its written in Ruby. Its fast and uses vim
style keybindings. 

The help system is launched with "?" and is pretty useful.  You can preload key
directories in the config in ~/.config/ranger/rc.conf file. So, for example, you
could type "g4" to immediately go to the directory
"/Users/zenn/prj/c060/launch/app4" by adding the line below.

```sh
map g4 cd /Users/zenn/prj/c060/launch/app4
```


# Methods

# Results

Sample reference. @Pocock1975a

Sample reference. @ranger1

