---
title: "Factors are confusing."
categories:
  - vim
  - R 
description: |
  A short description of the post.
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
    affiliation: InferenceX
    affiliation_url: https://inferenceX.com
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    self_contained: false
draft: true
bibliography: '`r normalizePath("~/shr/library.bib")`'
---

```{r setup, include=FALSE}
options(dplyr.print_max = 1e9)
library(pacman)

p_load(PerformanceAnalytics, quantmod, dygraphs, rmarkdown, tibble, broom,
       snakecase, tidyr, data.table,colorout, conflicted, purrr,ztable,
       hrbrthemes,readr, dplyr, magrittr, lubridate, zoo, mi, survival, ggplot2,
       printr, lsmeans, ggthemes,  knitr, xtable, doBy, nlme, reshape2,  pander,
       pwr, tufte)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/shr/zz.tools.R')
options(scipen = 1, digits = 2)
knitr::opts_chunk$set(echo = FALSE)
```



# Introduction

I've been using R for a while now and I have (like many of my colleagues)
wrestled with factors frequently. I have on occasion found them useful
particulary in defining an order among categorical variables. see example 2
below, but more often they have been a hassle to deal with rather than a help. 

The typical scenario is when a data set is read from a csv file and the input
function (e.g. read.csv() ) decides to declare a numeric variable to be a
factor. and categorical variable which should be categorical are defined as
factors. 

Why does this happen? Why is it necessary to use the readAsFactor=False flag in
order to get the more sensible behavior. 

Lets look back at some of the correspondence between R core members to see what
the original thinking was... 

Consider the following data set (borrowed from 
https://www.tutorialspoint.com/r/r_factors.htm

```{r}

# Create the vectors for data frame.
height <- c(132,151,162,139,166,147,122)
weight <- c(48,49,66,53,67,52,40)
gender <- c("male","male","female","female","male","female","male")

# Create the data frame.
input_data <- data.frame(height,weight,gender)
print(input_data)

# Test if the gender column is a factor.
print(is.factor(input_data$gender))

# Print the gender column so see the levels.
print(input_data$gender)




```

Running the above on the tutorialspoint web site gives a true response for
is.factor(gender). But when I run it I get a false. The web site indicates R
version 3.4.1 is being run. My version is 4.1.2.

Interesting. Did the default change somewhere along the line? Let check the
release notes. for 4.1

Sample reference section reference. @Pocock1975a

# Methods

# Results

## Prepare for analyses
```{r echo=T }
set.seed(1234)
library(ggplot2)
library(lattice)
```

```{r echo=T, message=FALSE}
library(PerformanceAnalytics)
library(quantmod)
library(dygraphs)

# Function to calculate monthly returns on a stock 
monthly_stock_returns <- function(ticker, start_year) {
  
  # Download the data from Yahoo finance
  symbol <- getSymbols(ticker, src = 'yahoo', 
                       auto.assign = FALSE, warnings = FALSE)
  
  # Tranform it to monthly returns using quantmode::periodReturn
  data <- periodReturn(symbol, period = 'monthly', 
                       subset=paste(start_year, "::", sep = ""),
                       type = 'log')

  # Let's rename the column of returns to something intuitive because
  # the column name is what will eventually be displayed
  colnames(data) <- as.character(ticker)

  # We want to be able to work with the xts objects so let's explicitly
  # assign them into the global environment using ticker name 
  assign(ticker, data, .GlobalEnv)
}
```





Let's graph the individual performances of each stock over time.

```{r, echo=T, layout="l-page"}
# Before we combine these into a portfolio, graph the individual returns
# and see if anything jumps out as unusual. It looks like something 
# affected Google in March of 2014, but didn't affect JP Morgan or Amazon.
dygraph(merged_returns, main = "Google v JP Morgan v Amazon") %>%
  dyAxis("y", label = "%") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))
```
```{r, echo=T, layout="l-screen"}
# Before we combine these into a portfolio, graph the individual returns
# and see if anything jumps out as unusual. It looks like something 
# affected Google in March of 2014, but didn't affect JP Morgan or Amazon.
dygraph(merged_returns, main = "Google v JP Morgan v Amazon") %>%
  dyAxis("y", label = "%") %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))
```


```{r, layout="l-body-outset"}
library(rmarkdown)
paged_table(mtcars, options = list(rows.print = 5))
```

<aside>
This content will appear in the gutter of the article.
</aside>




<aside>
```{r}
ggplot(mtcars, aes(hp, mpg)) + geom_point() + geom_smooth()
```
</aside>`



```{r}
oil_daily <- Quandl("FRED/DCOILWTICO", type = "raw", collapse = "daily",  
                    start_date="2006-01-01", end_date="2017-02-28")
# Now weekely and let's use xts as the type.
oil_weekly <- Quandl("FRED/DCOILWTICO", type = "xts", collapse = "weekly",  
                     start_date="2006-01-01", end_date="2017-02-28")
# And monthly using xts as the type.
oil_monthly <- Quandl("FRED/DCOILWTICO", type = "xts", collapse = "monthly",  
                      start_date="2006-01-01", end_date="2017-02-28")

oil_6month <- forecast(oil_monthly, h = 6)
oil_forecast_data <- data.frame(date = seq(mdy('03/01/2017'), 
                                           by = 'months', length.out = 6),
                                Forecast = oil_6month$mean,
                                Hi_95 = oil_6month$upper[,2],
                                Lo_95 = oil_6month$lower[,2])

head(oil_forecast_data)
```
