---
title: "unix tools for DS developers"
categories:
  - R 
  - AdvR answers
description: |
  A new article created using the Distill format.
author:
  - name: Ronald Glenn Thomas
    url: https://focusonR.org
    affiliation: InferenceX
    affiliation_url: https://rgthomaslab.com
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: '`r normalizePath("~/share/library.bib")`'
draft: true
---

```{r  include=FALSE}
options(dplyr.print_max = 1e9)
library(pacman)
p_load(tibble, broom, snakecase, tidyr, data.table,colorout, conflicted,
       purrr,ztable, hrbrthemes,readr, dplyr, magrittr, 
       lubridate, zoo, mi, survival, ggplot2, printr,
       lsmeans, ggthemes,  knitr, xtable, doBy, nlme,
       reshape2,  pander, pwr, tufte)

opts_chunk$set(warning = F, message = F, echo=F, fig.width=3.2,
	       fig.height=3,  results='asis', dev='pdf',
	       opts_chunk$set(cache.path = "cache/"))
source('~/share/zz.tools.R')
options(scipen = 1, digits = 2)
knitr::opts_chunk$set(echo = FALSE)
```



# Introduction This is the first of hopefully a number of posts
describing the setup of a number of essential tools for working with
data.table in a unix environment.  My most common usage of the
todonotes package, is to insert an uncustomized todonotes somewhere in
a latex document. An example of this usage is the command Sample
reference section reference. [@Pocock2005].

# Methods
A careful reading of the chapter. Reference additional references
including: 

# Results
Notes and offered solutions. 


# References









```{r , include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.


